testaddtreedim_DRAFT

### 2021-07-20 R/TreeFelling_Draft.Rmd
Fetched version 20-07-21

inventory <- treeselection(inventory, SpeciesCriteria, type = "manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE, objectivelax = FALSE, otherloggingparameters = loggingparameters())$inventory

speciescriteria = SpeciesCriteria
type = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
otherloggingparameters = loggingparameters()
# MainTrail

@@

if (fuel == "0" && directionalfelling != "1"){
  inventory <- inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Accessible == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails

@@

  inventory <- inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

@@

  inventory <- inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(otherloggingparameters$TreefallSuccessProportion, 1-otherloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

>>>>

inventory <- treeselection(inventory, SpeciesCriteria, scenario = "manual", fuel = "0",objective = 20, diversification = TRUE, specieslax = FALSE, objectivelax = FALSE, advancedloggingparameters = loggingparameters())$inventory

speciescriteria = SpeciesCriteria
scenario = "manual"
fuel = "2"
objective = 20
diversification = TRUE
directionalfelling = "2"
specieslax = FALSE
objectivelax = FALSE
advancedloggingparameters = loggingparameters()
# MainTrail

@@

if (fuel == "0" && directionalfelling != "1"){
  inventory <- inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Accessible == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Accessible = linked by 2ndtrails

@@

  inventory <- inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

@@

  inventory <- inventory %>% 
    mutate(TreeFellingOrientationSuccess = ifelse(Selected == "1"| ProbedHollow == "1", sample(c(1,0), size = 1, replace = F, prob = c(advancedloggingparameters$TreefallSuccessProportion, 1-advancedloggingparameters$TreefallSuccessProportion)), NA)) # Selected = not yet linked by 2ndtrails, because 2ndtrails came after

### 2021-07-20 R/Volume reviews functions.Rmd
Fetched version 20-07-21

Si type != "RIL3fuelhollow"  ou (type == "manual"& fuel !="2"): 
LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"

Si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"): NoHollowLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
LoggedVolume = ∑NoHollowLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".

@@

  NoHollowLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
  LoggedVolume <- sum(NoHollowLoggedVolume +
                        1-(otherloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
}

@@

si type = "RIL3fuel" ou (type == "manual"& fuel =="1"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*LoggedVolume

si type = "RIL3fuelhollow" ou (type == "manual"& fuel =="2"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowLoggedVolume

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + otherloggingparameters$Purge*LoggedVolume) # Damage and purge (0.14)

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + 
                    otherloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + otherloggingparameters$Purge*NoHollowLoggedVolume)
# damage + 1/3 of hollow trees volume + purge (0.14) of the healthy trees

>>>>

Si scenario != "RIL3fuelhollow"  ou (scenario == "manual"& fuel !="2"): 
LoggedVolume =∑TreeHarvestableVolume  des arbres codés "Logged"= "1"

Si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"): NoHollowLoggedVolume = ∑TreeHarvestableVolume  des arbres codés "Logged"= "1"
LoggedVolume = ∑NoHollowLoggedVolume  et ⅔ du volume de ceux codés ProbedHollow = "1".

@@

  NoHollowLoggedVolume <- sum(LoggedTable$TreeHarvestableVolume)
  LoggedVolume <- sum(NoHollowLoggedVolume +
                        1-(advancedloggingparameters$TreeHollowPartForFuel)*(HollowTable$TreeHarvestableVolume))
}

@@

si scenario = "RIL3fuel" ou (scenario == "manual"& fuel =="1"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause",  0,14*LoggedVolume

si scenario = "RIL3fuelhollow" ou (scenario == "manual"& fuel =="2"):
FuelVolume = ∑TreeHarvestableVolume  de bille des arbres codés "maintrail", "2ndtrail", "treefall2nd" ou "landing" dans la colonne "DeathCause", ⅓ du volume de la bille des arbres codés "hollowfuel" dans la colonne "DeathCause",  0,14*NoHollowLoggedVolume

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + advancedloggingparameters$Purge*LoggedVolume) # Damage and purge (0.14)

@@

FuelVolume <- sum(DamageTable$TreeHarvestableVolume + 
                    advancedloggingparameters$TreeHollowPartForFuel *(HollowTable$TreeHarvestableVolume) + advancedloggingparameters$Purge*NoHollowLoggedVolume)
# damage + 1/3 of hollow trees volume + purge (0.14) of the healthy trees

### 2021-07-20 R/testaddtreedim_DRAFT.Rmd
Fetched version 20-07-21

inventory = Paracou6_2016
crowndiameterparameters = ParamCrownDiameterAllometry
volumeparameters = ForestZoneVolumeParametersTable
otherloggingparameters = loggingparameters()

@@

  # TreeHarvestableVolume (m3)
  left_join(volumeparameters) %>%
  mutate(TreeHarvestableVolume = otherloggingparameters$TreeHarvestableVolumeAllometry(aCoef, bCoef, DBH)) %>%

  # TrunkHeight (m)
  mutate(TrunkHeight = otherloggingparameters$TrunkHeightAllometry(DBH, TreeHarvestableVolume)) %>%

  # TreeHeight (m)
  mutate(TreeHeight = otherloggingparameters$TreeHeightAllometry(DBH)) %>%

@@

# CrownDiameter (m)
# Add crown diameter allometry parameters at the inventory:
unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% # create ScientificName column in the inventory
  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% # at species scale
  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% # at genus scale
  left_join(famParamCrownDiameter, by = "Family") %>% # at family scale
  dplyr::rename(Taxo.family = Taxo, alpha.family = alpha, beta.family = beta) %>%
  # manage the different scales parameters Species > Genus > Family:
  # alpha:
  mutate(alpha = alpha.species, beta = beta.species, Taxo = Taxo.species) %>% # create the future & unique alpha,beta,taxo columns
  mutate(alpha = ifelse(is.na(alpha), alpha.genus, alpha)) %>% #if species parameters are absent, take genus parameters
  mutate(alpha = ifelse(is.na(alpha), alpha.family, alpha)) %>% #if species&genus parameters are absent, take family parameters
  mutate(alpha = ifelse(is.na(alpha), mean(alpha, na.rm =T), alpha)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-alpha.species, -alpha.genus, -alpha.family) %>% #remove obsolete columns
  # beta:
  mutate(beta = ifelse(is.na(beta), beta.genus, beta)) %>% #if species parameters are absent, take genus parameters
  mutate(beta = ifelse(is.na(beta), beta.family, beta)) %>% #if species&genus parameters are absent, take family parameters
  mutate(beta = ifelse(is.na(beta), mean(beta, na.rm =T), beta)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-beta.species, -beta.genus, -beta.family) %>% #remove obsolete columns
  # scale:
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>% #remove obsolete columns
  # compute the crown diameter
  mutate(CrownDiameter = otherloggingparameters$CrownDiameterAllometry(DBH, TreeHeight, alpha, beta))

>>>>

inventory = Paracou6_2016
crowndiameterparameters = ParamCrownDiameterAllometry
volumeparameters = ForestZoneVolumeParametersTable
advancedloggingparameters = loggingparameters()

@@

  # TreeHarvestableVolume (m3)
  left_join(volumeparameters) %>%
  mutate(TreeHarvestableVolume = advancedloggingparameters$TreeHarvestableVolumeAllometry(aCoef, bCoef, DBH)) %>%

  # TrunkHeight (m)
  mutate(TrunkHeight = advancedloggingparameters$TrunkHeightAllometry(DBH, TreeHarvestableVolume)) %>%

  # TreeHeight (m)
  mutate(TreeHeight = advancedloggingparameters$TreeHeightAllometry(DBH)) %>%

@@

# CrownDiameter (m)
# Add crown diameter allometry parameters at the inventory:
unite(Genus, Species, col = "ScientificName", sep = "_", remove = F) %>% # create ScientificName column in the inventory
  left_join(spParamCrownDiameter, by = c("ScientificName","Genus","Species")) %>% # at species scale
  left_join(genParamCrownDiameter, by = "Genus", suffix = c(".species", ".genus")) %>% # at genus scale
  left_join(famParamCrownDiameter, by = "Family") %>% # at family scale
  dplyr::rename(Taxo.family = Taxo, alpha.family = alpha, beta.family = beta) %>%
  # manage the different scales parameters Species > Genus > Family:
  # alpha:
  mutate(alpha = alpha.species, beta = beta.species, Taxo = Taxo.species) %>% # create the future & unique alpha,beta,taxo columns
  mutate(alpha = ifelse(is.na(alpha), alpha.genus, alpha)) %>% #if species parameters are absent, take genus parameters
  mutate(alpha = ifelse(is.na(alpha), alpha.family, alpha)) %>% #if species&genus parameters are absent, take family parameters
  mutate(alpha = ifelse(is.na(alpha), mean(alpha, na.rm =T), alpha)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-alpha.species, -alpha.genus, -alpha.family) %>% #remove obsolete columns
  # beta:
  mutate(beta = ifelse(is.na(beta), beta.genus, beta)) %>% #if species parameters are absent, take genus parameters
  mutate(beta = ifelse(is.na(beta), beta.family, beta)) %>% #if species&genus parameters are absent, take family parameters
  mutate(beta = ifelse(is.na(beta), mean(beta, na.rm =T), beta)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-beta.species, -beta.genus, -beta.family) %>% #remove obsolete columns
  # scale:
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.genus, Taxo)) %>% #if species parameters are absent, take genus parameters
  mutate(Taxo = ifelse(is.na(Taxo), Taxo.family, Taxo)) %>% #if species&genus parameters are absent, take family parameters
  mutate(Taxo = ifelse(is.na(Taxo), "mean", Taxo)) %>% #if species,genus&family parameters are absent, take parameters mean
  select(-Taxo.species, -Taxo.genus, -Taxo.family) %>% #remove obsolete columns
  # compute the crown diameter
  mutate(CrownDiameter = advancedloggingparameters$CrownDiameterAllometry(DBH, TreeHeight, alpha, beta))
